%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Reduce spacing after section
\titlespacing\section{0pt}{12pt}{10pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemOne}[1]{
  \item\small{#1}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small{#3} & \small{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & \small{#4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubheadingNoTitle}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 %\\
      % \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubSubItem}[1]{\resumeItemOne{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\textbf{\href{https://www.linkedin.com/in/kunlinhan/}{\LARGE {Kunlin Han}}} \\
{
    \href{mailto:{kunlinha@usc.edu}}{{kunlinha@usc.edu}} $|$ Phone: \href{tel:{}}{123-456-7890} $|$ \href{https://www.linkedin.com/in/kunlinhan/}{Linkedin (kunlinhan)}  $|$ \href{https://github.com/Karl-Han}{Github (Karl-Han)}  $|$ \href{https://www.iwktd.com/}{Detailed Resume} 
}\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
    {University of Southern California (USC)}{Los Angeles, CA}
    {Master of Electrical Engineering (MS Honors Fellow); GPA: 4.0/4.0
}{Dec 2021 - Dec 2023}
\resumeSubheading
    {South China Normal University (SCNU)}{Guangzhou, China}
    {Bachelor of Network Engineering; GPA: 3.78/4.0; Rank: 1/72
}{Sep 2017 - Jun 2021}
\resumeSubHeadingListEnd



\section{SKILLS}
\textbf{Programming Languages}: Python, C/C++, Verilog, VHDL, SystemVerilog, Tcl, Perl, Java, Rust, SQL\\ 
\textbf{Libraries}: Scrapy, BeautifulSoup, Requests, Pyrogram, Django\\ 
\textbf{EDA Tools}: Virtuoso, Spectre, QuestaSim, Calibre, Intel Quartus, Xilinx Vivado, Innovus, StarRC, PrimeTime\\ 
\textbf{Protocols}: AXI, PCIe, MOESI \hspace{\fill} \textbf{Tools:} UNIX, Linux, VIM, Git, Docker, Makefile\\ 


\section{PROJECTS}
\resumeSubHeadingListStart
\resumeSubheadingNoTitle
    {Branch Predictor and Prefetcher Implementation and Simulation}{Aug 2023 - Oct 2023}
\resumeItemListStart
	\resumeItemOne{Implemented and simulated bimodal predictor and correlated-branch predictor with Pin Tool to compare performance on benchmarks.}
	\resumeItemOne{Designed and explored design space by trading off cache hierarchy, execution unit and issue width on OoO CPU on gem5, and achieve 25\% higher throughput with 5\% extra transistor count comparing with the baseline design.}
	\resumeItemOne{Studied and simulated prefetchers, including Markov predictor, content-directed prefetcher and access map pattern matching prefetcher.}
\resumeItemListEnd
\resumeSubheadingNoTitle
    {Tomasulo Out-of-Order CPU Design}{Jun 2023 - Aug 2023}
\resumeItemListStart
	\resumeItemOne{Implemented Issue Unit, 2-stage Dispatch Unit, Re-Order Buffer and FPGA-friendly Copy-Free Check Pointing for FRAT and RRAT.}
	\resumeItemOne{Integrated, synthesized and programmed the overall system on Xilinx Artix-7 FPGA board.}
	\resumeItemOne{Validated the correctness of design with both simulation and on-chip logic analyzer (Chipscope).}
\resumeItemListEnd
\resumeSubheadingNoTitle
    {512-bit 6T SRAM Array Design}{Jan 2023 - May 2023}
\resumeItemListStart
	\resumeItemOne{Designed and drew layout of 1-bit SRAM cell, row/column decoder, sense amplifier, write driver, precharge circuit, latch and flip-flop with Cadence Virtuoso and GPDK 45nm.}
	\resumeItemOne{Achieved the Read SNM of 210 mV and Write SNM of 395 mV by proper sizing with VDD=1V.}
	\resumeItemOne{Integrated components into 4 8x16-bit SRAM banks to construct a 512-bit SRAM Array with the area of 2208 $nm^2$ in 2.6 Ghz (cycle time=0.4 ns).}
	\resumeItemOne{Measured the power consumption with Spectre, in which the average consumption for reading is 21.2 fJ, the average consumption for writing is 342 fJ and leakage is 20 fJ.}
	\resumeItemOne{Validated the correctness of all aforementioned components with vector file in Spectre and passed DRC and LVS.}
\resumeItemListEnd
\resumeSubheadingNoTitle
    {Extendable Asynchronous SNN Accerlator Design}{Jan 2023 - May 2023}
\resumeItemListStart
	\resumeItemOne{Designed extendable asynchronous SNN accelerator in SystemVerilog with SystemVerilogCSP library on a 5x5 filter and 25x25 ifmap with stride=1.}
	\resumeItemOne{Implemented configurable fork-join computation module for partial computation.}
	\resumeItemOne{Integrated computation modules with two memory modules on a deterministic mesh network.}
	\resumeItemOne{Verified correctness of computation module and the accelerator separately with timestep=2 in QuestaSim.}
\resumeItemListEnd
\resumeSubHeadingListEnd



\section{EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading
    {CS Department, USC}{Los Angeles, CA}
    {Graduate Teaching Assistant}{May 2022 - Aug 2022}
\resumeSubHeadingListEnd



\section{LEADERSHIP AND INVOLVEMENT}
\resumeSubHeadingListStart
\resumeSubheading
    {Hope Center, Reality L.A.}{Los Angeles, CA}
    {Volunteer}{Mar 2022 - Aug 2022}
\resumeSubheading
    {Network Club, SCNU}{Guangzhou, China}
    {Vice President of Technical Department}{Sep 2017 - Jun 2019}
\resumeSubHeadingListEnd



\end{document}